%کلمات کلیدی انگلیسی
\latinkeywords{Internet of Things, Predictive Maintenance, Industrial Internet of Things, Cyber-Physical Systems Maintenance}
%چکیده انگلیسی

\en-abstract{
In recent years, the internet of things has become one of the most popular technology topics. The application of this technology in all areas of human life, as well as recent developments in the fields of data collection, network and artificial intelligence, have made the internet of things to become the focus of many researchers. One of the challenges in industries and factories is the optimal replacement of parts. Due to the lack of sufficient information to analyze the condition of the parts, the appropriate solution to ensure the operation of the production line is to use experts to inspect the condition of the equipment or replace them regardless of their current conditions and only according to a previous schedule. In addition to not being accurate, these solutions impose many expenses and time on industries. In this project, we intend to provide a framework for analyzing equipment vibration data by using a combination of internet of things and artificial intelligence, so that it can be used to predict the remaining useful lifetime of parts. Also, using the web-based dashboard, the results can be shown to experts so that they can provide detailed planning for equipment maintenance and repair. By using this approach, the cost and time spent on replacing parts will be significantly reduced.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}